My title

### 2024-03-11 paper/paper.qmd
update change
Update paper.qmd

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git>."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# Introduction
Cooperative Election Study (CES) (@main_data) aims to study American electoral dynamics during 2022 elections period

# Data {#sec-data}
For the actual data we can use the 2022 Cooperative Election Study (CES) (@main_data)

@@

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git>."
date: today
date-format: long
abstract: 
There is no other nation in the world that conducts elections the way the United States does. Local government representatives oversee elections in around 8,000 distinct jurisdictions. They are then under the general supervision of authorities, who are frequently selected through election procedures or partisan appointees. Typically, the voter liaison at the polling place is a temporary worker who works unpaid for a single day and only gets a few hours of training. These distinctive characteristics of our electoral system, along with the fact that Americans vote more frequently than citizens in other countries on a wider range of issues and positions, create special difficulties for the efficient administration of elections that voters across demand and deserve.
None of the other nations' electoral systems display all or any of these traits, but none have the same mix of US administrative traits. The quality of administration differs from jurisdiction to jurisdiction and even from polling place to polling place because of decentralization and dependence on volunteers. Because partisan officials will be involved, accusations of partisanship regarding the rules or their interpretation may arise based on the outcome of the judgments made by the officials and who stands to gain from it. The quantity and variety of democratic options in protracted elections have outpaced voters' attention spans and cognitive capacities. These distinguishing characteristics of our voting system contribute to the issues seen in the most recent elections. This paper is mainly based on the 2022 US election.
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# Introduction
The goal of the Cooperative Election Study (CES) is to investigate how Americans vote and perceive their electoral experiences, how they hold their representatives accountable in elections, and how their behavior and experiences vary depending on the political climate and social milieu. The study used an extremely large sample that allowed it to account for variations across different legislative districts. Actually, the sample size at the state level is sufficient to measure the voter preference distribution within the majority of states with a respectable degree of accuracy.
60 teams participated in 2022CES, which resulted in a 60,000-case generic content sample. 
Fall of 2022 saw the recruitment of study participants. Every research team invested in a 1,000-person nationwide sample survey from Redwood City, California-based YouGov. Two waves of interviewing were used for the 2022 survey. Pre-election surveys were filled out on the spot between September 29 and November 8. The post-election campaigning frenzy took place between November 10 and December 15. For every 1,000 respondents, half of the questions had common material while the other half were fully created and managed by each study team. Questions that are common to all team modules and have a sample size equal to the total sample size of all team modules make up common content. Every one of the sixty teams bought a 1,000-person survey. Every case was chosen online, and YouGov created a corresponding random sample for this investigation.
The first data release happened on March 20, 2023. The Harvard University database contains archived and accessible data from this investigation. Vote verification is included in data release 2 for all respondents.
The study on CES 2022 is still under progress. Using a large-scale national survey, the Collaborative Congressional Election project was founded in 2006 to investigate congressional elections and representation. The project built upon the analysis conducted by the Public Opinion Research and Training Lab at the Massachusetts Institute of Technology in 2005.
# Data {#sec-data}
For the actual data we can use the 2022 Cooperative Election Study (CES) (@main_data)

@@

## Sampling and Sampling Matching
The CES 2022 dataset is a sample of adult U.S. citizens, taken from a considerably larger population, rather than an exhaustive list of all possible cases in the target population. The sample was deliberately created to be a true reflection of the population of the United States and to capture the variations among the different legislative districts for in-depth examination in the majority of states.
Through the Internet, YouGov conducted the CES 2022 survey. 60,000 adults were interviewed between September and November 2022 (pre-election data) and November and December 2022 (post-election data) for the Common Opinion. The YouGov matching approach for random sampling was used. YouGov employed the matched random sampling method at CES among other sampling techniques. The first step in this process is to count the target population, which in the case of general population research consists of all adults. This is typically done by using an extensive survey such as the American Community Survey. The target sample is then selected at random by CES from this target population. 
However, because it is frequently impractical to make direct contact with these individuals, a matching sample is chosen from among selectable respondents who share the same characteristics as the target sample. This selection process is carried out based on a multitude of attributes available in the voter and consumer databases.
## Weightening
A weighting process is used to account for any residual imbalances between the matched samples, therefore rigorously verifying the representativeness of CES samples. The weighting of the sample was adjusted to align with the framework's distribution along several demographic and political aspects. Entropy balancing and iterative proportional fitting (sequencing) of multiple important variables and their interactions comprise the first stage of the weighting process. The sample is also thought to be representative of every state for the survey's common content and takes into account changes for statewide political races.
There are two steps involved in selecting samples when utilizing the matching approach. First, select a sample at random from the intended audience. This sample is known as the target sample. The process of choosing a "representative" sample from a non-random sample of responders is known as sample matching. Although it works well for Web access panels, it may also be applied to other survey kinds, such phone surveys. The target population is enumerated before sample matching begins. All adults are the target group for general population studies, and they can be counted using either a top-notch survey like the American Community Survey or the decennial Census. This is referred to as a sampling frame in other contexts, although unlike traditional sampling, the sample is not taken out of the frame. 
Using traditional sampling, participants in the study are chosen at random from a framework for sampling. Because not every person in the framework has access to contact information, particularly email addresses, and because declining to participate would raise the expense of sampling in this manner, it could not be practical or cost-effective.
##Vote Vaildation
